Robust Adaptation to Multi-Scale Climate Variability

### 2019-04-08 report-earths-future/paper-2018-robust-adaptation-cyclical-risk.tex
tweak key point

% Key Points
\begin{keypoints}
  \item \add{Quasi-periodic and secular climate signals with different identifiability and predictability control uncertainty and risk into the future}
  \item \add{Adaptation strategies need to consider how the bias and variance in these risk predictions influences choices and decisions pathways}
  \item \add{Stylized experiments reveal how bias and variance of climate risk estimates over a finite planning periodinfluence risk mitigation}
\end{keypoints}

>>>>

% Key Points
\begin{keypoints}
  \item \add{Quasi-periodic and secular climate signals, with different identifiability and predictability, control future uncertainty and risk}
  \item \add{Adaptation strategies need to consider how uncertainties in risk projections influence success of decision pathways}
  \item \add{Stylized experiments reveal how bias and variance of climate risk projections influence risk mitigation over a finite planning period}
\end{keypoints}
